---
title: 'Assignment 02: Complex Numbers'
author: 'Kenji Sato^[Kobe University. mail@kenjisato.jp]'
date: '`r format(Sys.time(), "%d %B, %Y")`'
output:
  bookdown::pdf_document2:
    fig_caption: yes
    keep_tex: no
    latex_engine: pdflatex
    number_sections: yes
    template: null
    toc: no
  bookdown::html_document2: default
documentclass: scrartcl
---

# Overview

## Purpose {-}

The purpose of this assignment is as follows.

1. To learn how to use R as a calculator.
2. To learn basic properties of complex numbers.

## Instructions {-}

In this assignment, you will

- clone the assignment repository and make a working branch (eg. `solution` branch);
- solve the problems in Section 3; 
- write the solutions in `solution.Rmd`; 
- commit `solution.Rmd` and `solution.pdf`; and 
- open a Pull Request.
 
# Exercise

Let 
$$
\begin{aligned}
z_1 &= 2 - i \\
z_2 &= -1 + 2i.
\end{aligned}
$$

1. Calculate $z_1 + z_2$, $z_1 - z_2$, $z_1 z_2$, $z_1 / z_2$ and $z_1^3$. 
   Do it with pen and ppaper and write solutions with LaTeX syntax.
2. Use R to check the above calculatons are correct.


## Solution {-}

1.
$$
\begin{aligned}
z_1 + z_2 &= 1 + i,\\
z_1 - z_2 &= 3 - 3i,\\
z_1 z_2 &= 5i, \\
z_1 / z_2 &= - \frac{4}{5} - \frac{3}{5} i \\
z_1 ^ 3 &= 2 - 11i.
\end{aligned}
$$
2. Assignment:  
    ```{r}
    z1 <- 2 - 1i
    z2 <- -1 + 2i
    ```  
   Addition:   
    ```{r}
    z1 + z2
    ```  
   Subtraction:  
    ```{r}
    z1 - z2
    ```  
   Multiplication:
    ```{r}
    z1 * z2
    ```
   Division:
    ```{r}
    z1 / z2
    ```
   Power:
    ```{r}
    z1 ^ 3
    ```

\pagebreak

# Problems

## (1) {-}

Let 
$$
\begin{aligned}
z_1 &= 3 + i \\
z_2 &= 1 - i.
\end{aligned}
$$

1. Calculate $z_1^2 z_2^3$. 
   Do it with pen and ppaper and write solutions with LaTeX syntax.
2. Use R to check the above calculatons are correct.


## (2) {-}

It is always advisable to put blank spaces around operators. For example, you should always write `x <- 1 + 2` not `x<-1+2`. Although the latter is a legal code, those esthetic spaces increase readability and reduce bugs. 

The following code, however, is not allowed:

```{r, eval=FALSE}
z <- 1 + 2 i
```

1. Guess what happens if you try to run this code.
2. Run this code and interpret the error message.
3. Report what happened and why. 


## (3) {-}

A general form of complex numbers is $a + bi$, $a, b \in \mathbb R$. When $b = 1$, we usually omit $1$ and simply write as $a + i$; when $b = -1$ we write as $a - i$. In R, we cannot use such expressions as

```{r, eval=FALSE}
z <- 1 + i
w <- 1 - i 
```

1. Guess what happens if you try to run these codes.
2. Run these codes and interpret the error message.
3. Report what happened and why. 
