---
title: 'Assignment 02: Complex Numbers'
author: 'Your name^[Affiliation]'
date: '`r format(Sys.time(), "%d %B, %Y")`'
output:
  bookdown::pdf_document2:
    fig_caption: yes
    includes:
      in_header: asset/latex/custom.sty
    keep_tex: no
    latex_engine: pdflatex
    number_sections: yes
    template: null
    toc: no
  bookdown::html_document2: default
documentclass: scrartcl
---

# (1) {-}

Let 
$$
\begin{aligned}
z_1 &= 3 + i \\
z_2 &= 1 - i.
\end{aligned}
$$

1. Calculate $z_1^2 z_2^3$. 
   Do it with pen and paper and write solutions with LaTeX syntax.
2. Use R to check the above calculations are correct.

## Solution {-}
<!-- Write Solution to (1) Here -->







<!-- End of Solution to (1) -->

# (2) {-}

It is always advisable to put blank spaces around operators. For example, you should always write `x <- 1 + 2` not `x<-1+2`. Although the latter is a legal code, those esthetic spaces increase readability and reduce bugs. 

The following code, however, is not allowed:

```{r, eval=FALSE}
z <- 1 + 2 i
```

1. Guess what happens if you try to run this code.
2. Run this code and interpret the error message.
3. Report what happened and why. 

## Solution {-}
<!-- Write Solution to (2) Here -->




<!-- End of Solution to (2) -->

# (3) {-}

A general form of complex numbers is $a + bi$, $a, b \in \mathbb R$. When $b = 1$, we usually omit $1$ and simply write as $a + i$; when $b = -1$ we write as $a - i$. In R, we cannot use such expressions as

```{r, eval=FALSE}
z <- 1 + i
w <- 1 - i 
```

1. Guess what happens if you try to run these codes.
2. Run these codes and interpret the error message.
3. Report what happened and why. 


## Solution {-}
<!-- Write Solution to (3) Here -->






<!-- End of Solution to (3) -->

